Title

### 2020-12-02 documents/DraftReport.Rmd
posterior median figure

>>>>

```{r load results, results = 'hide', message = FALSE}

# test <- readRDS(here::here('data', 'out1_1.Rdata'))

#true vals
truth <- readRDS(here::here('data', 'scenarios.Rdata')) 
colnames(truth) <- gsub(' ', '', colnames(truth))
true.vals <- truth %>%
  dplyr::select(ScenarioNumber, MRdetection, Abunddetection, AdultSurv, JuvSurv, Dailynestsurvival, Fec) %>%
  dplyr::rename(scenario = ScenarioNumber) %>%
  reshape2::melt(id.vars = c('scenario'), value.name = 'Truth') %>%
  transform(variable = factor(variable,
                              levels = c('AdultSurv', 'JuvSurv', 'MRdetection', 'Fec', 'Abunddetection', 'Dailynestsurvival'),
                              labels = c('AdultSurv', 'JuvSurv', 'MRdetection', 'Fec', 'Abunddetection', 'Dailynestsurvival')))

#posterior medians for fec, mean.p, mean.phi[1:2], p.surv, phi.nest

#read in scenarios separately without mean.p below
sc <- c(1:5, 11:15)
niter <- 25

meds <- data.frame()
for (s in sc) {
  for (i in 1:niter) {

temp <- data.frame(readRDS(file = here::here('data', paste0('out', s, '_', i, '.Rdata')))) 
temp.med <- data.frame(t(apply(temp, 2, median)))
temp.med$iter <- i
temp.med$scenario <- s

meds <- rbind(meds, temp.med)
  }
}

sc <- c(6:10)
niter <- 25

meds2 <- data.frame()
for (s in sc) {
  for (i in 1:niter) {

temp <- data.frame(readRDS(file = here::here('data', paste0('out', s, '_', i, '.Rdata')))) 
temp.med <- data.frame(t(apply(temp, 2, median)))
temp.med$iter <- i
temp.med$scenario <- s

meds2 <- rbind(meds2, temp.med)
  }
}

meds <- bind_rows(meds, meds2)

post.meds <- meds %>% transform(scenario = factor(scenario)) %>%
  reshape2::melt(id.vars = c('scenario', 'iter')) %>%
  filter(variable %in% c('mean.phi.1.', 'mean.phi.2.', 'mean.p', 'fec', 'p.surv', 'phi.nest')) %>%
  transform(variable = factor(variable,
                              levels = c('mean.phi.1.', 'mean.phi.2.', 'mean.p', 'fec', 'p.surv', 'phi.nest'),
                              labels = c('JuvSurv', 'AdultSurv', 'MRdetection', 'Fec', 'Abunddetection', 'Dailynestsurvival')))

ggplot(post.meds, aes(y = value, x = scenario, group = scenario)) +
  geom_boxplot() +
  geom_point(size = 0.7, col = 'darkgrey') + 
  geom_point(data = true.vals, aes(y = Truth, x = scenario, group = scenario), col = 'darkred') +
  xlab('Scenario') + ylab('Posterior medians') +
  facet_wrap(~variable, scales = 'free_y') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))
